Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-13 ms.tex
abstract tweaks, small discussion change

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci.
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm
\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an
orbital period of 33 days.
\anytodo{Anything we should add?}
\end{abstract}

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.  
We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
an implementation of the affine-invariant ensemble sampler of 
\citet{Goodman10}
for each host star conditioned on the observed 
photometric properties as presented in \ref{Table:photometry}, with 
the exception of the W4 band, which we leave out this analysis due to 
its unreliability.

@@

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new general-purpose implementation of the \citet{Morton12} procedure, 
to calculate false positive probabilities (FPPs) for each of these 
K2 candidates.  We impose the following constraints on false positive
scenarios:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere within
an 8 arcsecond radius from the target star.
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail below).
\end{itemize}

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth]{f2}}
\caption{AO data for all systems imaged. 
The main frame for each single system shows the deep, saturated image.
The inset for each single system shows a shallower, unsaturated image to better
identify companions at close projected orbital separations.
For the two systems with imaged companions, EPIC 201546283 and 201828749,
only unsaturated frames are collected.
All subplots, including insets, are plotted on the same scale.}
\label{fig:AO}
\end{figure*}

@@

\subsection{Known Background Stars}
The P3K AO system has a field of view of $3.84 \times 3.84$ arcseconds.
\btmtodo{Check with Brendan to make sure he used this mode}.
Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds.
A background eclipsing binary within a few \KT\ pixels of our target
stars could mimic a transit signal while evading detection by P3K.
Such wide eclipsing binaries should appear in seeing-limited ground-based
surveys.

@@

We have presented stellar parameters for all planet candidates systems observed by
\paperit, validating \Nvalidated\ of the 36 candidates as bona fide planets and
\Nfp\ as bona fide false positives.

@@

We are grateful to the entire Kepler team, past and present.
Their tireless efforts were all essential to the tremendous success of the mission and the
successes of K2, present and future.

>>>>

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci.
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm
\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an
orbital period of 33 days.
We also present \texttt{vespa}, a new general-purpose implementation
of the \citet{Morton12} procedure to calculate false positive probabilities
for \KT\ candidates.
\end{abstract}

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.  
We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
an implementation of the affine-invariant ensemble sampler of 
\citet{Goodman10}
for each host star conditioned on the observed 
photometric properties as presented in Table 1.

@@

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new general-purpose implementation of the \citet{Morton12} procedure, 
to calculate false positive probabilities (FPPs) for each of these 
\KT\ candidates.  We impose the following constraints on false positive
scenarios:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere within
an 8 arcsecond radius from the target star.
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail below).
\end{itemize}

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth]{f2}}
\caption{AO data for all systems imaged. 
The main frame for each single system shows the deep, saturated image.
The inset for each single system shows a shallower, unsaturated image to better
identify companions at close projected orbital separations.
For the two systems with imaged companions, EPIC 201546283 and 201828749,
only unsaturated frames are collected.
All subplots, including insets, are plotted on the same scale.}
\label{Fig:AO}
\end{figure*}

@@

\subsection{Known Background Stars}
The PHARO AO system has a field of view of NUMBER arcseconds.
\btmtodo{Check with Brendan to find this number}.
Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds.
A background eclipsing binary within a few \KT\ pixels of our target
stars could mimic a transit signal inside our aperture while evading detection 
by PHARO.
Such wide eclipsing binaries should appear in seeing-limited ground-based
surveys.

@@

We have presented stellar parameters for all planet candidates systems observed by
\paperit, validating \Nvalidated\ of the 36 candidates as bona fide planets and
\Nfp\ as bona fide false positives. 
Of these planets, 4 have been previously validated in other works, while 17 are 
validated here for the first time.

@@

We are grateful to the entire Kepler team, past and present.
Their tireless efforts were all essential to the tremendous success of the mission and the
successes of \KT\, present and future.
